\textbf{EECS 340: Assignment 2}

### 2020-02-02 assignment_2/article.tex
✨ Add sketch answer to Problem 1(c2), a narrower version of (c1).
✨ Add sketch answer to Problem 1(d1).

>>>>

Since it is given that $\log(f(n))\geq 0$, $\log(g(n)) \geq 1 $, thus we must have:

Thus we may conclude $log(f(n)) = O(\log(g(n))$, the statement is therefore proven to be valid.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(d1) $f(2n) = \Theta(f(n))$}

Since it is known that $f(n) \geq 0$, $g(n) \geq 0$, and $c > 0$; we must have a constant $c' > 0$ which satisfy:

\paragraph{Case 1} Assume $f(n) \neq 0$.

\begin{gather}
    c' \geq \frac{f(2n)}{f(n)} \\
    \Rightarrow f(2n) \leq c'(f(n))
\end{gather}

Thus we may conclude $f(2n) = O(f(n))$.

Similarly, we may also have a constant $c'' > 0$ which satisfy:

\begin{gather}
    c'' \leq \frac{f(2n)}{f(n)} \\
    \Rightarrow f(2n) \geq c''(f(n))
\end{gather}

Thus we may conclude $f(2n) = \Omega(f(n))$.\newline

Since both the $O$- and $\Omega$-notation are established, we may therefore conclude $f(2n) = \Theta(f(n))$ in this case.

\paragraph{Case 1} Assume $f(n) = 0$ for $\all n$.

Thus we must have two constants $k_{1}, k_{2}$ which satisfy:
\begin{gather}
    f(2n) = 0 \\
    k_{1}(0) \leq f(2n) \leq k_{2}f(n)\Rightarrow k_{1}(0) \leq 0 \leq k_{2}(0), \ \forall k \in \mathbb{R^+}
\end{gather}

Thus we may conclude $f(2n) = \Theta(f(n))$.\newline

Since both cases reach to the conclusion of $f(2n) = \Theta(f(n))$, we have proven the statement to be valid.
